Standard Deviation Outcome Change - DEVELOPMENT

### 2023-04-27 minos/outcomes/standard_deviation_change_SF12.Rmd
Added smoothed loess lines to the marginal distribution plots, and added knitted RMarkdown html files in outcomes to .gitignore

@@

```{r}
# combine before we plot
b.2030$scen <- 'baseline'
i.2030$scen <- 'living_wage'

@@

```{r}
p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
  geom_point() +
  theme(legend.position = c(0.15, 0.9))

p1 <- ggMarginal(p, type='density', groupColour = TRUE)
p1
```

```{r}
p2 <- ggMarginal(p, type='histogram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p2
```

```{r}
p3 <- ggMarginal(p, type='densigram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p3
```

>>>>

base <- read_singular_local_out(out.path, 'baseline')
#int <- read_singular_local_out(out.path, 'livingWageIntervention')
int <- read_singular_local_out(out.path, 'energyDownlift')
```

@@

```{r}
# combine before we plot
b.2030$scen <- 'baseline'
i.2030$scen <- 'energyDownlift'

@@

```{r}
p <- ggplot(data = merged, aes(x = initial, y = end, group = scen, color = scen)) +
  geom_point(alpha = 0.6, size=0.1) +
  geom_smooth() +
  theme(legend.position = c(0.15, 0.9))

p1 <- ggMarginal(p, type='density', groupColour = TRUE)
p1

ggsave(filename = 'scatter_marg_dens_energy.png',
       plot = p1,
       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
```

```{r}
p2 <- ggMarginal(p, type='histogram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p2

ggsave(filename = 'scatter_marg_hist_energy.png',
       plot = p2,
       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
```

```{r}
p3 <- ggMarginal(p, type='densigram', groupColour = TRUE, xparams = list(position = 'dodge'), yparams=list(position = 'dodge'))
p3
ggsave(filename = 'scatter_marg_densigram_energy.png',
       plot = p3,
       path = '/home/luke/Documents/WORK/MINOS/TEST_PLOTS/')
```

```{r}

```
